Inspecting {glmnet} performances

### 2021-11-12 analysis/inspect-glmnet-models.Rmd

# load drake objects
loadd(
  benchmark_models_new_penalized_mbo_buffer2,
  task_new_buffer2
)
```

@@

obs_train_f4 <- as.matrix(task_new_buffer2[[2]]$env$data[train_inds_fold4, getTaskFeatureNames(task_new_buffer2[[2]])])
target_f4 <- getTaskTargets(task_new_buffer2[[2]])[train_inds_fold4]
```

@@

obs_pred_f4 <- as.matrix(task_new_buffer2[[2]]$env$data[pred_inds_fold4, getTaskFeatureNames(task_new_buffer2[[2]])])

@@

```{r}
truth <- task_new_buffer2[[2]]$env$data[pred_inds_fold4, "defoliation"]

@@

```{r}
lrn <- makeLearner("regr.cvglmnet", alpha = 0)
task_f4 <- subsetTask(task_new_buffer2[[2]], train_inds_fold4)

@@

>>>>

# load drake objects
loadd(
  benchmark_models_new_penalized_mbo_buffer2,
  task,
  task_reduced_cor
)
```

@@

obs_train_f4 <- as.matrix(task[[2]]$env$data[train_inds_fold4, getTaskFeatureNames(task[[2]])])
target_f4 <- getTaskTargets(task[[2]])[train_inds_fold4]
```

@@

obs_pred_f4 <- as.matrix(task[[2]]$env$data[pred_inds_fold4, getTaskFeatureNames(task[[2]])])

@@

```{r}
truth <- task[[2]]$env$data[pred_inds_fold4, "defoliation"]

@@

```{r}
lrn <- makeLearner("regr.cvglmnet", alpha = 0)
task_f4 <- subsetTask(task[[2]], train_inds_fold4)

@@

## Train/predict via {glmnet} manually on dataset with filtered feature correlation

obs_train_f4 <- as.matrix(task_reduced_cor[[2]]$env$data[train_inds_fold4, getTaskFeatureNames(task_reduced_cor[[2]])])
target_f4 <- getTaskTargets(task_reduced_cor[[2]])[train_inds_fold4]
```

obs_pred_f4 <- as.matrix(task_reduced_cor[[2]]$env$data[pred_inds_fold4, getTaskFeatureNames(task_reduced_cor[[2]])])

```{r}
truth <- task_reduced_cor[[2]]$env$data[pred_inds_fold4, "defoliation"]
